---
title: "simpleRegress"
author: "put your name here"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


## Model LENGTH~WEIGHT 


```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```
Comparing this plot to the previous one, we can say that the length can be better predicted by the bear's neck rather than it's weight because the residual standard error of the first plot is smaller than that of the second plot.  

## Model LENGTH~AGE
```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

Given that the residual standard error of this scatter plot is higher than that of the first plot and the adjusted R-squared of this plot is smaller than that of the first plot, therefore, the neck size is still the best variable that can predict a bear's length so far. 
## Model LENGTH~HEAD WIDTH
  
```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```
  
Same with the plot before this, head width is not a good variable to predict a bear's length. This is because the residual standard error is way higher than that of the first plot, and the adjusted R-square value is lower than that of the first plot. 

## Model LENGTH~HEAD LENGTH

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```



The points on the scatter plot appear to be tighter compared to the previous plots. Moreover, the residual standard error is 4.235 which is lower than that of the first plot, and the adjusted R-squared value is higher than that of the first plot. Therefore, head length is a better variable than neck in determining the length of a bear. 




